Asymmetric relationships and their effects on coexistence

### 2023-01-31 paper/Paper.Rnw
small changes

%header material for paper
\title{Asymmetric relationships and their impact on coexistence}
\date{}

@@

MCT and its recent computational extensions \citep{Ellner_2016,Ellner_2019} 
quantify the contributions of 
multiple mechanisms to coexistence. But we show below
that, for purely temporal variation, only one mechanism relates to tail associations: storage effects. 
So we begin by defining storage effects. 
The storage effect for species $i$ is the contribution of covariation between $E$ and 
$C$ to a difference between rare and common species mean growth rates, when $i$ is rare.
Specifically, storage effects for species $i$ are 
\begin{equation}
\Delta_i^{(EC)} = (\olr_{i\bs i} - q_{ij} \olr_{j \bs i})-(\olrs_{i \bs i}-q_{ij} \olrs_{j \bs i}),\label{eq:storage_effects_gen}
\end{equation}
where: $\olr_{i \bs i}$ refers to the mean ``growth when rare'' (GWR) of species $i$, that is, the mean growth rate of 
species $i$ when it is at negligible abundance and species $j$ (the other species) is at stochastic steady state;
$\olr_{j \bs i}$ refers to the mean steady-state 
growth rate of species $j$ when species $i$ is absent or at negligible abundance (this is $0$, \emph{a priori});
and $\olrs_{i \bs i}$ and $\olrs_{j \bs i}$ are analogous quantities, but for an alternative modelling scenario, identical except that
influences of environment and competition on either species have been rendered independent.  
A subscript 
$i \bs i$ always indicates a quantity computed for species $i$ when that species is at negligible abundance, and 
a subscript $j \bs i$ indicates a quantity computed for $j$ when $i$ is absent.
The \emph{scaling factor}
$q_{ij}$ measures the relative sensitivities to competition of the two species, see \cite{Chesson_1994},
\cite{Ellner_2016} and SI section \ref{SI-SIsect:scaling_factors} for the two
alternative definitions of $q_{ij}$ that we use. 
Since it was assumed that $r_i=r_i(E_i,C_i)$, we can write $\olr_{i \bs i}=\E[r_i(E_i,C_{i \bs i})]$, where
$\E(\cdot)$ denotes expected value just as does an overbar, but we use $\E$ for longer expressions.
Also, $\olr_{j \bs i}=\E[r_j(E_j,C_{j \bs i})]$.
An expression for $\olrs_{i \bs i}$ is obtained from $\olr_{i \bs i}$ by replacing the bivariate random 
variable $(E_i,C_{i \bs i})$ by a random variable with the same marginal distributions, but independent components, 
$(E_i^\shp,C_{i \bs i}^\shp)$, so $\olrs_{i \bs i}=\E[r_i(E_i^\shp,C_{i \bs i}^\shp)]$.
Likewise, $\olrs_{j \bs i}=\E[r_j(E_j^\shp,C_{j \bs i}^\shp)]$.

@@

The other mechanisms in MCT that apply in our modelling context of purely temporal variation
make no reference to covariation between quantities, whereas ATAs are 
defined in a covariation context. Therefore, storage effects are the only mechanism of coexistence
for which ATAs are relevant. Mathematical details supporting this claim are in SI section 
\ref{SI-SIsect:other_mechanisms}, but we here provide a conceptual understanding. \cite{Ellner_2016} and
\cite{Ellner_2019} provide a decomposition of the coexistence metric $\olr_{i \bs i} -q_{ij}\olr_{j \bs i}$,
which equals GWR of species $i$. The decomposition, which we use below, is similar to and motivated by the 
original decomposition of \cite{Chesson_1994}; the decomposition is how the mechanisms of 
coexistence operating in a given case are illuminated. The decomposition is 
\begin{equation}
\olr_{i \bs i} -q_{ij}\olr_{j \bs i}=\Delta_i^0+\Delta_i^E+\Delta_i^C+\Delta_i^{(E\shp C)}+\Delta_i^{(EC)},\label{eq:previous_decomp}
\end{equation}
where: $\Delta_i^0$ is a baseline;
$\Delta_i^E$ is a contribution to coexistence of environmental variation;
$\Delta_i^C$ is a contribution to coexistence of variation in competition;
$\Delta_i^{(E\shp C)}$ is a contribution to coexistence of having simultaneous variation in both environment and competition, but not including the effects 
of covariation in these quantities; and
$\Delta_i^{(EC)}$ is a contribution to coexistence of $EC$ covariation itself -- storage effects. 
Only storage effects involve $EC$ covariation,
so the only mechanism of coexistence influenced by ATA between $E$ and $C$ is storage effects. Combining our decomposition 
(\ref{eq:storage_effects_further}) with the decomposition (\ref{eq:previous_decomp}) of \cite{Ellner_2019} gives 
\begin{equation}
\olr_{i \bs i} -q_{ij}\olr_{j \bs i}=\Delta_i^0+\Delta_i^E+\Delta_i^C+\Delta_i^{(E\shp C)}+\Delta_i^{[E \nat C]} + \Delta_i^{[EC]},\label{eq:full_decomp}
\end{equation}
which is the extension of MCT which was goal G1 of the Introduction.

@@

To pursue goal G2 of the Introduction, we applied the framework of Theory to the lottery model, 
comparing the magnitude of the ATA effect on coexistance, $\Delta_i^{[EC]}$, to the magnitudes 
of the other terms of 
the decomposition (\ref{eq:full_decomp}) for various model parameterizations. We used two versions 
of the lottery model which we now specify. The versions both used the same dynamical equations
(Introduction) and assumed temporally independent and identically distributed (iid) fecundities, but the
versions differed in the distribution of $(B_1,B_2)$ used. Both distributions were based on 
transformations of the distributions $(b_1,b_2)$ pictured in Fig. \ref{fig:pedagog1}a-c;
the details of how the left- (Fig. \ref{fig:pedagog1}a), right- (Fig. \ref{fig:pedagog1}c), 
and symmetrically (Fig. \ref{fig:pedagog1}b) tail associated alternatives for $(b_1,b_2)$ were generated 
are in SI section \ref{SI-sect:noise}.

The \emph{log-normal fecundities lottery model} used $B_i = \exp(\sigma+\mu_i b_i)$,
and therefore had parameters $\sigma$, $\mu_1$ and $\mu_2$ in addition to the death rate parameter $\delta$
that both versions of the lottery model use (Introduction). The parameter $\sigma$ is the variance of the
log-fecundities and $\mu_i$ is the mean log fecundity for species $i$.

The \emph{beta-fecundities lottery model}
used $B_i = \eta_i F_\beta \circ \varphi^{-1}(b_i)$, where $\varphi$ is the CDF of the standard normal
distribution and $F_\beta$ is the CDF of a beta distribution 
with shape and scale parameters $0.5$ (probability density function proportional to $x^{-05}(1-x)^{-0.5}$ on
the unit interval). So the beta-fecundities model had parameters $\eta_1$, $\eta_2$ and $\delta$,
and produced fecundities with $U$-shaped distributions between $0$ and $\eta_1$, for $B_1$, and
$\eta_2$, for $B_2$. The mean fecundity for species $i$ was $\eta_i/2$ and larger $\eta_i$ also 
corresponded to more variable fecundities for species $i$.

For both versions of the lottery model, 
fecundities were taken to directly reflect 
the environment, i.e., the $E_i$ of Theory was set equal to $B_i$. 
Competition, $C_i(t)$, in the lottery model occurs at the stage of juveniles occupying open sites.
For both model versions, $C_i$ was therefore taken to be the number of new offspring
divided by the number of open sites, $C_i(t)=( B_1(t)N_1(t)+B_2(t)N_2(t) )/(\delta N$), which
does not depend on $i$. These choices for $E$ and $C$ meet the assumptions of Theory (SI section Y).
%***DAN: This SI reference is to the big section S$ listed below, but this material will be in the
%first part of that section, prior to the subsections.

\subsection{Plotting results for G2}

%Then write a para or section that starts by saying we plotted the decomp terms against model parameters for
%the log-normal-fecundity lottery model, and some mathematical shortcuts simplified it. Then summarize
%the shortcuts.
%This is similar to an existing para. Also cites a lot of sup mat stuff.

%Then a similar para for the beta-fecundity lottery model.

%Then a para about ATA exclusion and rescue and how that was assess for each model - different from
%the current way of doing it with trait spaces - drop the trait space stuff.

@@

%G2
Left- or right-tail associated noise $(b_1,b_2)$, with $b_i$ normally distributed with mean $\mu_i$ and standard deviation 
$\sigma$, was generated as pictured in Fig. \ref{fig:noise}, details in SI section \ref{SI-sect:noise}.
To achieve goal G2 from the Introduction, i.e., to explore using a simple model the relative magnitudes of the contributions 
to coexistence that come from ATAs versus other mechanisms, we plotted the terms $\Delta_i^0$, $\Delta_i^E$, $\Delta_i^C$, 
$\Delta_i^{(E\shp C)}$, $\Delta_i^{[E \nat C]}$ and $\Delta_i^{[EC]}$ [see (\ref{eq:full_decomp})] for the lottery model
against the parameters of the model, $\mu_1$, $\mu_2$, $\sigma$ and $\delta$; and we compared 
values on plots. Some mathematical shortcuts, summarized here, simplified plotting. 
First, we assumed, without loss of generality, that $\mu_1 \leq \mu_2$. To understand coexistence, 
it was then sufficient to decompose the GWR of the weaker competitor, species 1. 
Second, we showed that, for the 
lottery model, none of the components in (\ref{eq:full_decomp}) depends independently on $\mu_1$ and $\mu_2$;
instead they depend only on $\mu_1-\mu_2$ (SI section \ref{SI-sect:math_simplifications}). So we plotted 
against $\mu_1 - \mu_2$. 
Third, we showed that the values of all components in (\ref{eq:full_decomp}) were the same 
for both our left- and right-tail associated noises (SI section \ref{SI-sect:math_simplifications}). So we only generated plots 
for left-tail associated noise. For each combination of $\delta=0.2, 0.4, 0.6, 0.8$
and $\mu_1-\mu_2=0,-0.5,-2,-4$,
we plotted all the components of (\ref{eq:full_decomp}) against $\sigma$. 
%Relative importance of contributions was judged from the 
%plots to assess whether and to what extent ATA effects on coexistence were meaningfully large for the lottery model, compared to 
%the contributions of other mechanisms.
Mathematical simplications for the $\delta=1$ case make it straightforward to see that
coexistence is impossible and that the case is relatively trivial (SI 
section \ref{SI-sect:delta1}), so that case is not plotted.  
The simulation methods of \cite{Ellner_2019} were used to compute the components of (\ref{eq:full_decomp}).
Computationally efficient means of performing these simulations, for the lottery model, are in 
SI section \ref{SI-sect:efficient_computation}.

@@

%***DAN: I edited the caption (2023 01 25) but need to replace the figure once I know where in the repo 
%structure it is generated and stored, and after I have re-run Jasmin's code
\begin{figure}
\includegraphics[width=.25\textwidth]{../results_figs/fig1_vertical.pdf}
\caption{Examples motivating our study of the effects of asymmetric tail associations (ATAs) on competition
and coexistence. (a-c) Bivariate random variables with standard normal marginals showing
alternative patterns of association in the left and right parts of the distributions. 
The two variables in (a) are more strongly related to each
other in the left parts of the distributions, termed ``left-tail association;'' those in (b) 
are symmetrically associated; and those in (c) 
are more strongly related to each other in the right parts, termed ``right-tail association''. All three cases have 
the same Pearson correlation, $\rho$, up to sampling variation, so Pearson correlation does not identify these 
very different patterns of association. For (a, c), we used asymmetrically tail associated cases which are perfectly 
correlated in the lower or upper halves of the distributions, though it is also possible to generate asymmetrically 
tail associated noise with imperfect correlations in both halves of the distributions [\citealp{Nelsen2006,Ghosh_2020_AER};
see also (g,h)]. 
The variables $(B_1,B_2)$ described in the Introduction and Methods were obtained by generating noise as 
pictured and then transforming the marginals as specified in Methods.
(d-f) Lottery model population simulations using $(B_1,B_2)$ obtained by transforming the 
respectively corresponding variables (a-c; see Introduction).
(g,h) Two examples of ATAs found in nature. Axes are population densities of two plankton species, 
\emph{Ceratium fusus} and \emph{Ceratium furca}, sampled in successive years in two of the 15 locations 
in the North Sea considered by \citep{Ghosh_2020_ecolevol}. ATAs differed by location, with (g) showing 
left-tail association and (h) showing right-tail association. \label{fig:pedagog1}}
\end{figure}

>>>>

%header material for paper
\title{Asymmetric relationships and their effects on coexistence}
\date{}

@@

MCT and its recent computational extensions \citep{Ellner_2016,Ellner_2019} 
quantify the contributions of 
multiple mechanisms to coexistence. But we show below
that, for purely temporal variation, only one mechanism relates to tail associations: storage effects. 
So we begin by defining storage effects. 
The storage effect for species $i$ is the contribution of covariation between $E$ and 
$C$ to a difference between rare and common species mean growth rates, when $i$ is rare.
Specifically, storage effects for species $i$ are 
\begin{equation}
\Delta_i^{(EC)} = (\olr_{i\bs i} - q_{ij} \olr_{j \bs i})-(\olrs_{i \bs i}-q_{ij} \olrs_{j \bs i}),\label{eq:storage_effects_gen}
\end{equation}
where: $\olr_{i \bs i}$ refers to the mean ``growth when rare'' (GWR) of species $i$, that is, the mean growth rate of 
species $i$ when it is at negligible abundance and species $j$ (the other species) is at stochastic steady state;
$\olr_{j \bs i}$ refers to the mean steady-state 
growth rate of species $j$ when species $i$ is absent or at negligible abundance (this is $0$, \emph{a priori});
and $\olrs_{i \bs i}$ and $\olrs_{j \bs i}$ are analogous quantities, but for an alternative modelling scenario, identical except that
influences of environment and competition on either species have been rendered independent.  
A subscript 
$i \bs i$ always indicates a quantity computed for species $i$ when that species is at negligible abundance, and 
a subscript $j \bs i$ indicates a quantity computed for $j$ when $i$ is absent.
The \emph{scaling factor}
$q_{ij}$ measures the relative sensitivities to competition of the two species. See \cite{Chesson_1994},
\cite{Ellner_2016} and SI section \ref{SI-SIsect:scaling_factors} for the two
alternative definitions of $q_{ij}$ that we use, but one definition is $q_{ij}=1$, and to understand the new
ideas presented here it is sufficient to use that definition. 
Since it was assumed that $r_i=r_i(E_i,C_i)$, we can write $\olr_{i \bs i}=\E[r_i(E_i,C_{i \bs i})]$, where
$\E(\cdot)$ denotes expected value just as does an overbar, but we use $\E$ for longer expressions.
Also, $\olr_{j \bs i}=\E[r_j(E_j,C_{j \bs i})]$.
An expression for $\olrs_{i \bs i}$ is obtained from $\olr_{i \bs i}$ by replacing the bivariate random 
variable $(E_i,C_{i \bs i})$ by a random variable with the same marginal distributions, but independent components, 
$(E_i^\shp,C_{i \bs i}^\shp)$, so $\olrs_{i \bs i}=\E[r_i(E_i^\shp,C_{i \bs i}^\shp)]$.
Likewise, $\olrs_{j \bs i}=\E[r_j(E_j^\shp,C_{j \bs i}^\shp)]$.

@@

The other mechanisms in MCT that apply in our modelling context of purely temporal variation
make no reference to covariation between quantities, whereas ATAs are 
defined in a covariation context. Therefore, storage effects are the only mechanism of coexistence
for which ATAs are relevant. Mathematical details supporting this claim are in SI section 
\ref{SI-SIsect:other_mechanisms}, but we here provide a conceptual understanding. \cite{Ellner_2016} and
\cite{Ellner_2019} provide a decomposition of the coexistence metric $\olr_{i \bs i} -q_{ij}\olr_{j \bs i}$,
which equals GWR of species $i$. The decomposition, which we use below, is similar to and motivated by the 
original decomposition of \cite{Chesson_1994}; the decomposition is how the mechanisms of 
coexistence operating in a given case are illuminated. The decomposition is 
\begin{equation}
\olr_{i \bs i} -q_{ij}\olr_{j \bs i}=\Delta_i^0+\Delta_i^E+\Delta_i^C+\Delta_i^{(E\shp C)}+\Delta_i^{(EC)},\label{eq:previous_decomp}
\end{equation}
where: $\Delta_i^0$ is a baseline;
$\Delta_i^E$ is a contribution to coexistence of environmental variation;
$\Delta_i^C$ is a contribution to coexistence of variation in competition;
$\Delta_i^{(E\shp C)}$ is a contribution to coexistence of having simultaneous variation in both environment and competition, but not including the effects 
of covariation in these quantities; and
$\Delta_i^{(EC)}$ is a contribution to coexistence of $EC$ covariation itself -- storage effects. 
Only storage effects involve $EC$ covariation,
so the only mechanism of coexistence influenced by ATA between $E$ and $C$ is storage effects. Combining our decomposition 
(\ref{eq:storage_effects_further}) with the decomposition (\ref{eq:previous_decomp}) of \cite{Ellner_2019} gives 
\begin{equation}
\olr_{i \bs i} -q_{ij}\olr_{j \bs i}=\Delta_i^0+\Delta_i^E+\Delta_i^C+\Delta_i^{(E\shp C)}+\Delta_i^{[E \nat C]} + \Delta_i^{[EC]},\label{eq:full_decomp}
\end{equation}
which is the extension of MCT that was goal G1 of the Introduction.

@@

%Setup - two versions, and basics which apply to both
To pursue goal G2 of the Introduction, we applied the framework of Theory to the lottery model, 
comparing the magnitude of the ATA effect on coexistance, $\Delta_i^{[EC]}$, to the magnitudes 
of the other terms of 
the decomposition (\ref{eq:full_decomp}) for various model parameterizations. We used two versions 
of the lottery model which we now specify. The versions both used the same dynamical equations
(Introduction) and assumed temporally independent and identically distributed (iid) fecundities, but the
versions differed in the distributions of $(B_1,B_2)$ used. Both distributions were based on 
transformations of the distributions $(b_1,b_2)$ pictured in Fig. \ref{fig:pedagog1}a-c;
the details of how the left- (Fig. \ref{fig:pedagog1}a), right- (Fig. \ref{fig:pedagog1}c), 
and symmetrically (Fig. \ref{fig:pedagog1}b) tail associated alternatives for $(b_1,b_2)$ were generated 
are in SI section \ref{SI-sect:noise}.

%the log-normal fecundities version
The \emph{log-normal fecundities lottery model} used $B_i = \exp(\sigma+\mu_i b_i)$,
and therefore had parameters $\sigma$, $\mu_1$ and $\mu_2$ in addition to the death rate parameter $\delta$
(Introduction) that both versions of the lottery model used. The parameter $\sigma$ is the variance of the
log-fecundities and $\mu_i$ is the mean log fecundity for species $i$.

%the beta fucundities version
The \emph{beta-fecundities lottery model}
used $B_i = \eta_i F_\beta^{-1} \circ \varphi(b_i)$, where $\varphi$ is the CDF of the standard normal
distribution and $F_\beta$ is the CDF of a beta distribution 
with shape and scale parameters $0.5$ (probability density function proportional to $x^{-05}(1-x)^{-0.5}$ on
the unit interval). So the beta-fecundities model had parameters $\eta_1$, $\eta_2$ and $\delta$,
and produced fecundities with $U$-shaped, beta distributions between $0$ and $\eta_1$, for $B_1$, and
$\eta_2$, for $B_2$. The mean fecundity for species $i$ was $\eta_i/2$, and larger $\eta_i$ also 
corresponded to more variable fecundities for species $i$.

%more stuff that applies to both
For both versions of the lottery model, 
fecundities were taken to directly reflect 
the environment, i.e., the $E_i$ of Theory was set equal to $B_i$. 
Competition, $C_i(t)$, in the lottery model occurs at the stage of juveniles occupying open sites.
For both model versions, $C_i$ was therefore taken to be the number of new offspring
divided by the number of open sites, $C_i(t)=( B_1(t)N_1(t)+B_2(t)N_2(t) )/(\delta N$), which
does not depend on $i$. These choices for $E_i(t)$ and $C_i(t)$ fulfill the assumption of Theory 
that the growth rate, $r_i(t)$ is an increasing function of $E_i(t)$ and a decreasing function of $C_i(t)$ 
(see SI section \ref{SI-SIsect:TheoryForLottery} for details).

\subsection{How results were plotted for G2}

%Plotting shortcuts for the log-normal fecundities model
To explore, using the log-normal fecundities lottery model, the relative magnitudes of the contributions 
to coexistence that come from ATAs versus other mechanisms, we plotted the terms of the decomposition 
(\ref{eq:full_decomp}) for that model against the model parameters $\mu_1$, $\mu_2$, $\sigma$ and $\delta$.
We labeled regions of the plot which corresponded to ATA rescue or exclusion, i.e., regions for which
GWR and GWR-$\Delta_i^{[EC]}$ had opposite signs.
Some mathematical shortcuts, summarized here, simplified plotting. 
First, we assumed, without loss of generality, that $\mu_1 \leq \mu_2$. To understand coexistence, 
it was then sufficient to decompose GWR of the weaker competitor, species 1. 
Second, we showed that, for the log-normal fecundities
lottery model, none of the components of (\ref{eq:full_decomp}) depends independently on $\mu_1$ and $\mu_2$;
instead they depend only on $\mu_1-\mu_2$ (SI section \ref{SI-sect:math_simplifications}). 
%***DAN: Not sure if this will the right citation anymore after we restructure those parts of the SI
So we plotted against $\mu_1 - \mu_2$. 
Third, we showed that the values of all components in (\ref{eq:full_decomp}) were the same 
for both our left- and right-tail associated noises (SI section \ref{SI-sect:math_simplifications}). 
%***DAN: Also check this citation
So we only generated plots 
for left-tail associated noise. For each combination of $\delta=0.2, 0.4, 0.6$
and $\mu_1-\mu_2=0,-0.5,-2,-4$,
we plotted the components of (\ref{eq:full_decomp}) against $\sigma$. 
%***DAN: Jasmin mentioned that she only used \delta=0.2, .4, .6 because of a comment Ellner made where he 
%said it was known that larger values of \delta made for very little storage effects. Read that comment 
%again and then write something here to jstify the choice. I think I can probably then delete the section of
%sup mat, mentioned in the commented text below, that talks about \delta=1.
%Mathematical simplications for the $\delta=1$ case make it straightforward to see that
%coexistence is impossible and that the case is relatively trivial (SI 
%section \ref{SI-sect:delta1}), so that case is not plotted.  
The simulation methods of \cite{Ellner_2019} were used to compute the components of (\ref{eq:full_decomp}).
Computationally efficient means of performing these simulations are in 
SI section \ref{SI-sect:efficient_computation}.
%***DAN: check the citation after restructuring the SI

%Then a similar para for the beta-fecundity lottery model.
To explore, using the beta fecundities lottery model, the relative magnitudes of the contributions 
to coexistence that come from ATAs versus other mechanisms, we plotted the terms of the decomposition 
(\ref{eq:full_decomp}) for that model against the model parameters $\eta_1$, $\eta_2$, and $\delta$.
%***DAN: finish it

@@

@@

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig1_a-h.pdf}
\caption{Examples motivating our study of the effects of asymmetric tail associations (ATAs) on competition
and coexistence. (a-c) Bivariate random variables with standard normal marginals showing
alternative patterns of association in the left and right parts of the distributions. 
The two variables in (a) are more strongly related to each
other in the left parts of the distributions, termed ``left-tail association;'' those in (b) 
are symmetrically associated; and those in (c) 
are more strongly related to each other in the right parts, termed ``right-tail association''. All three cases have 
the same Pearson correlation, $\rho$, up to sampling variation, so Pearson correlation does not identify these 
very different patterns of association. For (a, c), we used asymmetrically tail associated cases which are perfectly 
correlated in the lower or upper halves of the distributions, though it is also possible to generate asymmetrically 
tail associated noise with imperfect correlations in both halves of the distributions [\citealp{Nelsen2006,Ghosh_2020_AER};
see also (g,h)]. 
The variables $(B_1,B_2)$ described in the Introduction and Methods were obtained by generating noise as 
pictured and then transforming the marginals as specified in Methods.
(d-f) Lottery model population simulations using $(B_1,B_2)$ obtained by transforming the 
respectively corresponding variables (a-c; see Introduction).
(g,h) Two examples of ATAs found in nature. Axes are population densities of two plankton species, 
\emph{Ceratium fusus} and \emph{Ceratium furca}, sampled in successive years in two of the 15 locations 
in the North Sea considered by \citep{Ghosh_2020_ecolevol}. ATAs differed by location, with (g) showing 
left-tail association and (h) showing right-tail association. \label{fig:pedagog1}}
\end{figure}
